### 2020-03-17 Rmd/World_Map_Breeding_Systems.Rmd
Plot of breeding systems

@@

p <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="black") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub, cols = colnames(data_merged_sub[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub[,c(7:9)]),
                       labels = c("Hermaphroditism", "Dioecy", "Monoecy"),
                       values = c("Hermaphroditism" = "#4DAF4A",
                                  "Monoecy" = "#984EA3",
                                  "Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) +
  theme(legend.position = c(0.21, 0.009),
        legend.justification = c(1, 0),
        axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm"))

>>>>

data_merged_sub_ord <- data_merged_sub[order(data_merged_sub$Id_number),]
#Move coordinates manually to see all points (Improving plot visualization)
#Manual jitter
data_merged_sub_ord$Id_number <- seq(1, length(data_merged_sub_ord$Id_number))
#Fixing New Zealand pies
data_merged_sub_ord[19,4] <- -28
data_merged_sub_ord[19,3] <- 168
data_merged_sub_ord[20,4] <- -52
data_merged_sub_ord[20,3] <- 180
data_merged_sub_ord[21,4] <- -48
data_merged_sub_ord[21,3] <- 158

#Fixing Galapagos pies
data_merged_sub_ord[18,4] <- -7
data_merged_sub_ord[18,3] <- -105

data_merged_sub_ord[27,4] <- 6
data_merged_sub_ord[27,3] <- -105

#Fixing Mauritius pies
data_merged_sub_ord[13,4] <- -12
data_merged_sub_ord[13,3] <- 72
data_merged_sub_ord[17,4] <- -28
data_merged_sub_ord[17,3] <- 72

#Fixing Denmark pies
data_merged_sub_ord[3,4] <- 72
data_merged_sub_ord[4,4] <- 60
data_merged_sub_ord[7,4] <- 50

#Fixing Venezuela pies

data_merged_sub_ord[22,3] <- -45
data_merged_sub_ord[22,4] <- 10
data_merged_sub_ord[23,3] <- -45
data_merged_sub_ord[23,4] <- 25

#Fixing Japan pies

data_merged_sub_ord[11,3] <- 154
data_merged_sub_ord[14,3] <- 145
data_merged_sub_ord[14,4] <- 20

#Fixing Spain pies

data_merged_sub_ord[28,3] <- -20
data_merged_sub_ord[28,4] <- 28

data_merged_sub_ord[1,3] <- -20
data_merged_sub_ord[1,4] <- 52
data_merged_sub_ord[2,3] <- -30
data_merged_sub_ord[2,4] <- 40

#Fixing Argentina pies

data_merged_sub_ord[5,3] <- -90

#Fixing Brazil pies

data_merged_sub_ord[26,3] <- -30

#Fixing Sweden pies

data_merged_sub_ord[8,3] <- 40
data_merged_sub_ord[8,4] <- 78

#Fixing Denmark pies

data_merged_sub_ord[3,3] <- 0
data_merged_sub_ord[3,4] <- 80
data_merged_sub_ord[4,3] <- 15
data_merged_sub_ord[4,4] <- 80
data_merged_sub_ord[7,3] <- 45
data_merged_sub_ord[7,4] <- 60

#Fixing UK pies

data_merged_sub_ord[6,3] <- -8
data_merged_sub_ord[6,4] <- 67

#Fixing Australia

data_merged_sub_ord[12,3] <- 120

#Fixing China pie

data_merged_sub_ord[10,3] <- 90
data_merged_sub_ord[10,4] <- 0

#Fixing USA pie

data_merged_sub_ord[24,3] <- -60

#Fixing Canada pie
data_merged_sub_ord[25,3] <- -42
data_merged_sub_ord[25,4] <- 52
data_merged_sub_ord[15,3] <- -71
data_merged_sub_ord[15,4] <- 92

#Fixing Greenland pie

data_merged_sub_ord[16,4] <- 92
data_merged_sub_ord[9,4] <- 92

@@

p <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="grey", size=0.35) +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
 data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:9)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:9)]),
 labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
 "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding systems",subtitle = "",
  caption = "",fill = NULL) + theme(legend.position = c(0.215, 0.010),legend.justification = c(1, 0),
  axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +
  geom_segment(data = data_merged_sub_ord,aes(x = 168, y = -34, xend = 172, yend = -43),color = "black", size = 0.3, alpha = 0.8) + #NZ
  geom_segment(data = data_merged_sub_ord, aes(x = 179, y = -46, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
  geom_segment(data = data_merged_sub_ord, aes(x = 164, y = -48, xend = 172, yend = -43), color = "black",size = 0.3, alpha = 0.8) + #NZ
  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = 6, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) +  #GALAPAGOS
  geom_segment(data = data_merged_sub_ord, aes(x = -99, y = -7, xend = -90, yend = 0), color = "black", size = 0.3, alpha = 0.8) + #GALAPAGOS
  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -12), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
  geom_segment(data = data_merged_sub_ord, aes(x = 57, y = -20.5, xend = 66, yend = -28), color = "black", size = 0.3, alpha = 0.8) + #MAURITIUS
  geom_segment(data = data_merged_sub_ord, aes(x = -51, y = 10, xend = -61, yend = 5.5), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
  geom_segment(data = data_merged_sub_ord, aes(x = -51, y =25 , xend = -67, yend = 8.9), color = "black", size = 0.3, alpha = 0.8) + #VENEZUELA
  geom_segment(data = data_merged_sub_ord, aes(x = 148, y = 35, xend = 135.8, yend = 35), color = "black", size = 0.3, alpha = 0.8) + 
  geom_segment(data = data_merged_sub_ord, aes(x = 140, y = 22, xend = 129, yend = 28), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = -15.5, y = 32, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) + 
  geom_segment(data = data_merged_sub_ord, aes(x = -15, y = 50, xend = 3, yend = 43), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = -24, y = 40, xend = -6, yend = 37), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = -84, y = -32, xend = -68, yend = -32), color = "black", size = 0.3, alpha = 0.8) + 
  geom_segment(data = data_merged_sub_ord, aes(x = -36, y = -21, xend = -58, yend = -21), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = 34, y = 78, xend = 18.5, yend = 68), color = "black", size = 0.3, alpha = 0.8) + 
  geom_segment(data = data_merged_sub_ord, aes(x = 0, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = 15, y = 74.5, xend = 10, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = -8, y = 61, xend = 1.5, yend = 52), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = 39, y = 60, xend = 9, yend = 56), color = "black", size = 0.3, alpha = 0.8) +
  geom_segment(data = data_merged_sub_ord, aes(x = 126, y = -36, xend = 148, yend = -36), color = "black", size = 0.3, alpha = 0.8) + #AUS
  geom_segment(data = data_merged_sub_ord, aes(x = 90, y = 6, xend = 100, yend = 28), color = "black", size = 0.3, alpha = 0.8) + #CHINA
  geom_segment(data = data_merged_sub_ord, aes(x = -66, y = 39, xend = -89, yend = 39), color = "black", size = 0.3, alpha = 0.8) + #USA
  geom_segment(data = data_merged_sub_ord, aes(x = -48, y = 52, xend = -75, yend = 45), color = "black", size = 0.3, alpha = 0.8) + #CANADA
  geom_segment(data = data_merged_sub_ord, aes(x = -71, y = 86, xend = -71, yend = 81), color = "black", size = 0.3, alpha = 0.8) + #CANADA
  geom_segment(data = data_merged_sub_ord, aes(x = -52, y = 86, xend = -52, yend = 71), color = "black", size = 0.3, alpha = 0.8) + #GREENLAND
  geom_segment(data = data_merged_sub_ord, aes(x = -20, y = 86, xend = -20, yend = 74), color = "black", size = 0.3, alpha = 0.8)
